### 2014-03-14 src/analysis.Rnw
update

<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
o.stats.sel.xp$scope <- NA
r.stats.sel.xp$scope <- NA
o.stats.sel.xp$sampling <- NA
r.stats.sel.xp$sampling <- NA

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  return(x)
}

o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))

o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)

o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))

o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)

o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))

o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)

@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

@@

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())
o.xp <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

<<count>>=
stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
colnames(o.stats.sel.loc) <- new.colnames
colnames(r.stats.sel.loc) <- new.colnames

o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)

stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
colnames(o.stats.sel.loc.w) <- new.colnames
colnames(r.stats.sel.loc.w) <- new.colnames

o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)

@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

@@

\begin{figure*}[t]
<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:locsel}
\end{figure*}

\begin{figure*}[t]
<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
\label{fig:wlocsel}
\end{figure*}

@@

<<one>>=
stats.one <- subset(stats.rest, grepl('^o[.]', operator))

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames

o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)

r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)

@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

@@

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames

o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

o.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.op$operator))
r.stats.sel.op$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.op$operator))

o.stats.sel.op <- o.stats.sel.op[,c(1,7,2,3,4,5,6)]
r.stats.sel.op <- r.stats.sel.op[,c(1,7,2,3,4,5,6)]

#o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)

@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

>>>>

<<xpercentunit>>=
#1
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.xp.sample), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.xp.sample), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

@@

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}

\begin{figure*}[t]
<<x.per.sel.round,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts
@
\caption{The effect of round(x) reduction, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}
%Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.
% ----------------------------------------------------------------------

@@

<<count>>=
#2
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.loc), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.loc), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:lcountl}
\end{table*}

@@

\begin{figure*}[t]
<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:locsel}
\end{figure*}

\begin{figure*}[t]
<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts
@
\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
\label{fig:wlocsel}
\end{figure*}

@@

<<one>>=
#3
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(o.stats.sel.one), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(f(r.stats.sel.one), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The one per element selection criteria results.}
\label{tbl:onesel}
\end{table*}

@@

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
#4
@

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.op, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.op, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operators}
\label{tbl:operators}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.opsel, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.opsel, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {Operator Selection}
\label{tbl:opsel}
\end{table*}

### 2014-03-14 src/paper.Rnw
update

clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
% 10 pages for the main text + 1 for references.
<<introduction, child='introduction.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@

>>>>

clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
<<>>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
o.stats.sel.xp$scope <- NA
r.stats.sel.xp$scope <- NA
o.stats.sel.xp$sampling <- NA
r.stats.sel.xp$sampling <- NA

f <- function(x) {
  x <- x[,c(7,8,2,3,4,5,6)]
  return(x)
}

o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))

o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$scope <- gsub('.*_','', o.stats.sel.xp.sample$operator)
o.stats.sel.xp.sample$sampling <- gsub('_.*','', o.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$scope <- gsub('.*_','', r.stats.sel.xp.sample$operator)
r.stats.sel.xp.sample$sampling <- gsub('_.*','', r.stats.sel.xp.sample$operator)

o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))

o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$scope  <- gsub('.*_','', o.stats.sel.xp.round$operator)
o.stats.sel.xp.round$sampling  <- gsub('_.*','', o.stats.sel.xp.round$operator)
r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$scope  <- gsub('.*_','', r.stats.sel.xp.round$operator)
r.stats.sel.xp.round$sampling  <- gsub('_.*','', r.stats.sel.xp.round$operator)

o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))

o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$scope  <- gsub('.*_','', o.stats.sel.xp.ceil$operator)
o.stats.sel.xp.ceil$sampling  <- gsub('_.*','', o.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$scope  <- gsub('.*_','', r.stats.sel.xp.ceil$operator)
r.stats.sel.xp.ceil$sampling  <- gsub('_.*','', r.stats.sel.xp.ceil$operator)
# 1 done
stats.loc <- subset(stats.rest, grepl('^l[.]', operator))
o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^l[.]', operator))
colnames(o.stats.sel.loc) <- new.colnames
colnames(r.stats.sel.loc) <- new.colnames

o.stats.sel.loc$operator  <- gsub('l[.]1x','1/', o.stats.sel.loc$operator)
o.stats.sel.loc$scope  <- gsub('.*_','', o.stats.sel.loc$operator)
o.stats.sel.loc$sampling  <- gsub('_.*','', o.stats.sel.loc$operator)
r.stats.sel.loc$operator  <- gsub('l[.]1x','1/', r.stats.sel.loc$operator)
r.stats.sel.loc$scope  <- gsub('.*_','', r.stats.sel.loc$operator)
r.stats.sel.loc$sampling  <- gsub('_.*','', r.stats.sel.loc$operator)

stats.loc.w <- subset(stats.rest, grepl('^wl[.]', operator))
o.stats.sel.loc.w <- subset(o.f(stats.loc.w), select=sel.colnames)
r.stats.sel.loc.w <- subset(r.f(stats.loc.w), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^wl[.]', operator))
colnames(o.stats.sel.loc.w) <- new.colnames
colnames(r.stats.sel.loc.w) <- new.colnames

o.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', o.stats.sel.loc.w$operator)
o.stats.sel.loc.w$scope  <- gsub('.*_','', o.stats.sel.loc.w$operator)
o.stats.sel.loc.w$sampling  <- gsub('_.*','', o.stats.sel.loc.w$operator)
r.stats.sel.loc.w$operator  <- gsub('wl[.]1x','1/', r.stats.sel.loc.w$operator)
r.stats.sel.loc.w$scope  <- gsub('.*_','', r.stats.sel.loc.w$operator)
r.stats.sel.loc.w$sampling  <- gsub('_.*','', r.stats.sel.loc.w$operator)
# 2 done

stats.one <- subset(stats.rest, grepl('^o[.]', operator))

o.stats.sel.one <- subset(o.f(stats.one), select=sel.colnames)
r.stats.sel.one <- subset(r.f(stats.one), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^o[.]', operator))
colnames(o.stats.sel.one) <- new.colnames
colnames(r.stats.sel.one) <- new.colnames

o.stats.sel.one$operator  <- gsub('o[.]1x','1/', o.stats.sel.one$operator)
o.stats.sel.one$scope  <- gsub('.*_','', o.stats.sel.one$operator)
o.stats.sel.one$sampling  <- gsub('_.*','', o.stats.sel.one$operator)

r.stats.sel.one$operator  <- gsub('o[.]1x','1/', r.stats.sel.one$operator)
r.stats.sel.one$scope  <- gsub('.*_','', r.stats.sel.one$operator)
r.stats.sel.one$sampling  <- gsub('_.*','', r.stats.sel.one$operator)
# 3 done

stats.op <- subset(stats.rest, grepl('^(op:|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op:|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames

#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

o.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', o.stats.sel.op$operator)))
r.stats.sel.op$operator  <- gsub('NVMC','NMC', gsub('_','',gsub('op.*:','', r.stats.sel.op$operator)))

o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]

stats.opsel <- subset(stats.rest, grepl('^opsel', operator))
o.stats.sel.opsel <- subset(o.f(stats.opsel), select=sel.colnames)
r.stats.sel.opsel <- subset(r.f(stats.opsel), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^opsel', operator))
colnames(o.stats.sel.opsel) <- new.colnames
colnames(r.stats.sel.opsel) <- new.colnames

#o.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')
#r.stats.sel.op$kind  <- ifelse(grepl('opsel:', o.stats.sel.op$operator), 'selection', 'operator')

o.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', o.stats.sel.opsel$operator))
r.stats.sel.opsel$operator  <- gsub('_','',gsub('op.*:','', r.stats.sel.opsel$operator))

o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
# 4 done

@
% 10 pages for the main text + 1 for references.
<<introduction, child='introduction.Rnw'>>=
@
<<related, child='related.Rnw'>>=
@
